---
title: "lab4package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4package)
```

This package, designed for the "Advanced Programming in R" LiU course, contains the `linreg` class with the following methods:

- `print()`:  The `print()` method returns the coefficients and coefficient names from your linear model. 

- `plot()`: The `plot()` method returns two graphs, the first one representing the residuals versus the fitted values of your model solution.

- `resid()`: The `resid()` method returns the residuals' vector.    

- `pred()`: The `pred()` method returns the predicted values' vector.      

- `coef()`: The `coef()` method returns the coefficients.   

- `summary()`: The `summary()` method prints out the coefficients with their standard error, t-value and p-value. Additionally, it also shows the estimate of $\hat{\sigma}$ and the degrees of freedom of the model.  

To use the methods in the class we first have to create the object of that class by using `linreg$new()` and introducing a `formula` object and a `data.frame` object. Once this is done we can call the methods my writing the object's name followed by dollar sign and the name of the method.   
For a better understanding, see the following example.   

```{r}
linreg_obj <- linreg$new(Petal.Length ~ Species, data = iris)

linreg_obj$print()
linreg_obj$plot()
linreg_obj$pred()
linreg_obj$resid()
linreg_obj$coef()
linreg_obj$summary()
```

